---
title: "Polling Location Webscraper"
author: "Annika Kufrovich"
date: "July 14, 2020"
output: html_document
---


###Intro

This document will go through how to webscrape for a single Florida county's currently polling locations for each precinct from voterfocus.com. In this case we will be using Alachua. After that we'll scrape polling locations for all Florida counties (with the exception of Orange and Sarasota counties). For a basic guide on how to webscrape see this link: [https://www.analyticsvidhya.com/blog/2017/03/beginners-guide-on-web-scraping-in-r-using-rvest-with-hands-on-knowledge/]



##Alachua

Loading packages
```{r, message=FALSE, warning=FALSE}
library(rvest)
library(dplyr)
library(stringr)
```


reading in url
```{r}
url <- 'https://www.voterfocus.com/PrecinctFinder/precinctDirectory?county=FL-ALA'
webpage <- read_html(url)
```


Getting Precinct numbers. 
```{r}
#Using CSS selectors to scrape the precinct number section
number_data_html <- html_nodes(webpage,'.PageSection .Title')

#Converting the data to text
number_data <- html_text(number_data_html)

#Inspecting data
head(number_data)

##Converting to numeric vector
prec_numbers <- str_remove_all(number_data, "Precinct ")

```


Getting addresses
```{r}
#Using CSS selectors to scrape the address section
address_data_html <- html_nodes(webpage,'.NameAndAddress a')

#Converting the data to text
address_data <- html_text(address_data_html)

#Inspecting data
head(address_data)

##replacing \r\n\r\n\t\t\t\t\t\t\t\t\t with ", "
poll_address <- str_replace_all(address_data, "\r\n\t\t\t\t\t\t\t\t\t", ", ")
```


Getting location names (in case they are needed for crosschecking addresses later)

```{r}
#Using CSS selectors to scrape the address section
name_data_html <- html_nodes(webpage,'.Name')

#Converting the data to text
name_data <- html_text(name_data_html)

#Inspecting data
head(name_data)

##removing \r\n\r\n\t\t\t\t\t\t\t\t\t and \r\n\t\t\t\t\t\t\t\t
poll_name <- str_remove_all(name_data, "\r\n\t\t\t\t\t\t\t\t\t")
poll_names <- str_remove_all(poll_name, "\r\n\t\t\t\t\t\t\t\t")
head(poll_names)
```

Making a data frame

```{r}
ALApollplace <- data.frame(precinct = prec_numbers, address = poll_address, pollname = poll_names)
head(ALApollplace)
```




##Every Florida County

Making a vector of all the 3 letter endings for the voterfocus link. Leaving out Orange County and Sarasota County since they have no precinct polling locations displayed on this website. You can find official county abbreviations here: [https://floridaqsoparty.org/counties/counties-list/], however the voterfocus website uses the first 3 letters of the county name. (Will check later what abbreviations voter file has.)

```{r}
endings <- c("ALA", "BAK", "BAY", "BRA", "BRE", "BRO")

```

