---
title: "Polling Location Webscraper"
author: "Annika Kufrovich"
date: "July 14, 2020"
output: html_document
---


###Intro

This document will go through how to webscrape for a single Florida county's currently polling locations for each precinct from voterfocus.com. In this case we will be using Alachua. After that we'll scrape polling locations for all Florida counties (with the exception of Orange and Sarasota counties). For a basic guide on how to webscrape see this link: [https://www.analyticsvidhya.com/blog/2017/03/beginners-guide-on-web-scraping-in-r-using-rvest-with-hands-on-knowledge/]



##Alachua

Loading packages
```{r, message=FALSE, warning=FALSE}
library(rvest)
library(dplyr)
library(stringr)
```


reading in url
```{r}
url <- 'https://www.voterfocus.com/PrecinctFinder/precinctDirectory?county=FL-ALA' ##you could also use "", doesn't really matter
webpage <- read_html(url)
```


Getting Precinct numbers. 
```{r}
#Using CSS selectors to scrape the precinct number section
number_data_html <- html_nodes(webpage,'.PageSection .Title')

#Converting the data to text
number_data <- html_text(number_data_html)

#Inspecting data
head(number_data)

##Removing precinct string from all entries
prec_numbers <- str_remove_all(number_data, "Precinct ")

```


Getting addresses
```{r}
#Using CSS selectors to scrape the address section
address_data_html <- html_nodes(webpage,'.NameAndAddress a')

#Converting the data to text
address_data <- html_text(address_data_html)

#Inspecting data
head(address_data)

##replacing \r\n\r\n\t\t\t\t\t\t\t\t\t with ", "
poll_address <- str_replace_all(address_data, "\r\n\t\t\t\t\t\t\t\t\t", ", ")
```


Getting location names (in case they are needed for crosschecking addresses later)

```{r}
#Using CSS selectors to scrape the name section
name_data_html <- html_nodes(webpage,'.Name')

#Converting the data to text
name_data <- html_text(name_data_html)

#Inspecting data
head(name_data)

##removing \r\n\r\n\t\t\t\t\t\t\t\t\t and \r\n\t\t\t\t\t\t\t\t
poll_name <- str_remove_all(name_data, "\r\n\t\t\t\t\t\t\t\t\t")
poll_names <- str_remove_all(poll_name, "\r\n\t\t\t\t\t\t\t\t")
head(poll_names)
```

Making a data frame

```{r}
ALApollplace <- data.frame(precinct = prec_numbers, address = poll_address, pollname = poll_names, abr = c(rep("ALA", length(prec_numbers))), abrprecinct = paste0(c(rep("ALA", length(prec_numbers))), prec_numbers))
head(ALApollplace)
write.csv(ALApollplace, "alachuapollplace")
```




##Every Florida County

Making a vector of all the 3 letter endings for the voterfocus link. Leaving out Orange County and Sarasota County since they have no precinct polling locations displayed on this website. You can find official county abbreviations here: [https://floridaqsoparty.org/counties/counties-list/], however the voterfocus website mainly uses the first 3 letters or different abbreviations of the county name. (Will check later what abbreviations voter file has.)

```{r}
endings <- c("ALA", "BAK", "BAY", "BRA", "BRE", "BRO", "CAL", "CHA", "CIT", "CLA", "CLL", "CLM", "DAD", "DES", "DIX", "DUV", "ESC", "FLA", "FRA", "GAD", "GIL", "GLA", "GUL", "HAM", "HAR", "HEN", "HER", "HIG", "HIL", "HOL", "IND", "JAC", "JEF", "LAF", "LAK", "LEV", "LIB", "MAD", "MAN", "MRN", "MRT", "MON", "NAS", "OKA", "OKE", "OSC", "PAL", "PAS", "PIN", "POL", "PUT", "SAN", "SEM", "STJ", "STL", "SUM", "SUW", "TAY", "UNI", "VOL", "WAK", "WAL", "WAS")

leo_ending <- c("LEO") ##Doing separately since one of the precincts at the time of coding has no polling location information in such a way that it could mess up the webscraper (eg it won't scrape NA or an empty line for precinct 1201)
lee_ending <- c("LEE") ##similar issue for lee county but for multiple precincts


no_info_endings <- c("ORA", "SAR") ##Orange and Sarasota County's pages were empty as of 7/17/20

```


Main automated webscraper

```{r}
incomplete_url <- "https://www.voterfocus.com/PrecinctFinder/precinctDirectory?county=FL-"

##setting up empty vectors to be added to in for loop
countyabr <- c()
prec_nums <- c()
addresses <- c()
pollnames <- c()
lengthsequal <- c() ##this can be used with commented out lines of the for loop to test if you have an equal number of entries for precincts and any other data of interest in the webscraper, only works for 1 thing at a time in this format (eg only precinct number and addresses or precinct number and poll name). Vector should all be TRUE if everything is equal, any instances of false entries should be investigated

for(i in 1:length(endings)){
  webpage <- read_html(paste0(incomplete_url, endings[i])) ##reading county-specific webpage
  number.data.html <- html_nodes(webpage,'.PageSection .Title') ##scraping precint numbers
  number.data <- html_text(number.data.html) ##converting to text
  prec.numbers <- str_remove_all(number.data, "Precinct ") ##removing unnecesary part of string
  length <- length(prec.numbers) ##Needed to add county abbreviation for each precinct entry in next line
  countyabr <- c(countyabr, rep(endings[i], length)) ##Adding county abreviation for each entry, can be changed later to appropriate abbreviations for voter file
  prec_nums <- c(prec_nums, prec.numbers) ##Adding precinct numbers
  address.data.html <- html_nodes(webpage,'.NameAndAddress a') ##scraping addresses
  address.data <- html_text(address.data.html) ##converting to text
  poll.address <- str_replace_all(address.data, "\r\n\t\t\t\t\t\t\t\t\t", ", ") ##replacing unnecesary part of string
  addresses <- c(addresses, poll.address) ##adding to addresses vector
  #length2 <- length(poll.names)
  #lengthsequal[i] <- (length == length2)
  name.data.html <- html_nodes(webpage,'.Name') ##scraping poll names
  name.data <- html_text(name.data.html) ##converting to text
  poll.name <- str_remove_all(name.data, "\r\n\t\t\t\t\t\t\t\t\t") ##replacing unnecesary part of string
  poll.names <- str_remove_all(poll.name, "\r\n\t\t\t\t\t\t\t\t") ##replacing unnecesary part of string part 2
  pollnames <- c(pollnames, poll.names) ##adding to pollnames vector
  length3 <- length(poll.names)
  lengthsequal[i] <- (length == length3)
}
```


Webscraping odd counties, It's worth noting that these could have been incorporated into the main webscraper loop with if statements but I decided not to do this since the counties have 2 different problems. This may be done later

```{r}
##Leon county is missing data  for precinct 1201 (first listed), and for several other scattered precincts will fix this later

#webpage <- read_html(paste0(incomplete_url, leo_ending)) ##reading county-specific webpage, changed endings[i] to leo_ending
#number.data.html <- html_nodes(webpage,'.PageSection .Title') ##scraping precint numbers
#number.data <- html_text(number.data.html) ##converting to text
#prec.numbers <- str_remove_all(number.data, "Precinct ") ##removing unnecesary part of string
#length <- length(prec.numbers) ##Needed to add county abbreviation for each precinct entry in next line
#countyabr <- c(countyabr, rep(leo_ending, length)) ##Adding county abreviation for each entry, can be changed later to appropriate abbreviations for voter file, changed to leo_ending
#prec_nums <- c(prec_nums, prec.numbers) ##Adding precinct numbers
#address.data.html <- html_nodes(webpage,'.NameAndAddress a') ##scraping addresses
#address.data <- html_text(address.data.html) ##converting to text
#poll.address <- str_replace_all(address.data, "\r\n\t\t\t\t\t\t\t\t\t", ", ") ##replacing unnecesary part of string
#addresses <- c(addresses, c(NA, poll.address)) ##adding to addresses vector, putting one NA before address entries since the actual first precinct has no address
#length2 <- length(poll.names)
#lengthsequal[i] <- (length == length2)
#name.data.html <- html_nodes(webpage,'.Name') ##scraping poll names
#name.data <- html_text(name.data.html) ##converting to text
#poll.name <- str_remove_all(name.data, "\r\n\t\t\t\t\t\t\t\t\t") ##replacing unnecesary part of string
#poll.names <- str_remove_all(poll.name, "\r\n\t\t\t\t\t\t\t\t") ##replacing unnecesary part of string part 2
#pollnames <- c(pollnames, c(NA, poll.names)) ##adding to pollnames vector, same change as addresses line
#length3 <- length(poll.names)
#lengthsequal[i] <- (length == length3)


##Lee County has several empty precincts at the end

webpage <- read_html(paste0(incomplete_url, lee_ending)) ##reading county-specific webpage, changed to lee_ending
number.data.html <- html_nodes(webpage,'.PageSection .Title') ##scraping precint numbers
number.data <- html_text(number.data.html) ##converting to text
prec.numbers <- str_remove_all(number.data, "Precinct ") ##removing unnecesary part of string
length <- length(prec.numbers) ##Needed to add county abbreviation for each precinct entry in next line
countyabr <- c(countyabr, rep(lee_ending, length)) ##Adding county abreviation for each entry, can be changed later to appropriate abbreviations for voter file, changed to lee_ending
prec_nums <- c(prec_nums, prec.numbers) ##Adding precinct numbers
address.data.html <- html_nodes(webpage,'.NameAndAddress a') ##scraping addresses
address.data <- html_text(address.data.html) ##converting to text
poll.address <- str_replace_all(address.data, "\r\n\t\t\t\t\t\t\t\t\t", ", ") ##replacing unnecesary part of string
addresses <- c(addresses, poll.address) ##adding to addresses vector
#length2 <- length(poll.address)
#lengthsequal[i] <- (length == length2)
name.data.html <- html_nodes(webpage,'.Name') ##scraping poll names
name.data <- html_text(name.data.html) ##converting to text
poll.name <- str_remove_all(name.data, "\r\n\t\t\t\t\t\t\t\t\t") ##replacing unnecesary part of string
poll.names <- str_remove_all(poll.name, "\r\n\t\t\t\t\t\t\t\t") ##replacing unnecesary part of string part 2
length3 <- length(poll.names) #uncommented and moved up to add appropriate amount of NAs
pollnames <- c(pollnames, c(poll.names, rep(NA, (length - length3)))) ##adding to pollnames vector, adding NAs to the end by the difference in lengths
#lengthsequal[i] <- (length == length3)

FLpollplace <- data.frame(abr = countyabr, precinct = prec_nums, address = addresses, pollname = pollnames, abrprecincts = paste0(countyabr, prec_nums))
head(FLpollplace)
write.csv(FLpollplace, "FLPollPlace")
```





